%-----------------------------------------------------------------------------%

% Letter class
\documentclass[a4paper, 10pt]{letter}
\usepackage[margin=0.5in]{geometry}
% Name of sender
\name{Analabha Roy}

% Signature of sender
\signature{Analabha Roy\\Asst Prof.,  Dept. Phys. BU}

% Address of sender
\address
{
Department of Physics, The University of Burdwan,\\
	Golapbag, Bardhaman $713104$, India.
}

%-----------------------------------------------------------------------------%

\begin{document}
	
	% Name and address of receiver
	\begin{letter}
		{
			The Editor(s),\\
			Physical Review B,\\
			American Physical Society, USA.
		}
		
		% Opening statement
		\opening{Dear Editor(s),}
		\bigskip
		\textbf{RE: Referee comments for manuscript BH14505}
		\bigskip\noindent\\
	On behalf of myself and all other authors of the above-mentioned manuscript, I thank the referees for their thorough evaluation, constructive feedback, and ideas that enhanced our presentation. Please find attached an amended manuscript that addresses their issues. Finally, we provide thorough responses to their comments.	
		
		% Closing statement
		\closing{Yours Sincerely,}



\ps
P.S. I'm sorry for the delay. The referee responses arrived during my Dussehra vacation abroad. After I returned to university in late October, our research team could begin responding and amending the manuscript. I trust the review process is unaffected by this delay. - AR


\encl{
\begin{enumerate}
\item Revised manuscript \# BH14505.
\item Authors' responses to reviewers' comments.
\end{enumerate}
}

		
	\end{letter}
\end{document}
